PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-07-07 manuscript_00.Rmd
bug fix

@@

load('data/diff_data_pull.Rdata') # from src/diff_data_pull.R
toc()
```

@@

```{r scEiaD_data_overview, fig.height = 35, fig.width = 25, echo = F, message = F, fig.cap=scEiaD_data_overview_cap}
tic()
num1 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num2 <- meta_filter %>% filter(Organ != 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num3 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(CellType) %>% unique() %>% length()
scEiaD_data_overview_cap <- fig_cap(name = 'scEiaD_data_overview', caption = glue::glue("Distribution of tissues and cell types in scEiaD. A. tabulation of the number of cells present across {num1} ocular and {num2} non-ocular tissues, B. Number of studies for each ocular tissue. C. Number of cells present across {num3} curated ocular-derived cell types."))

@@

exp_plot_giga<- make_exp_plot(input, scEiaD_2020_v01, meta_filter)

input$exp_plot_genes <- up
exp_plot_iovs <- make_exp_plot(input, scEiaD_2020_v01, meta_filter)
a_legend <- get_legend(exp_plot_giga)
plot_grid(plot_grid(exp_plot_giga + theme(legend.position="none") + xlab(''),
          exp_plot_iovs + theme(legend.position="none") + ylab('') + xlab(''), labels = c('a','b')),
          a_legend, ncol = 1, rel_heights = c(1,0.2))
#toc()
```

>>>>

load('data/diff_data_pull.Rdata') # from src/diff_data_pull.R

@@

toc()
```

@@

```{r scEiaD_data_overview, fig.height = 35, fig.width = 25, echo = F, message = F, fig.cap=scEiaD_data_overview_cap}

num1 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num2 <- meta_filter %>% filter(Organ != 'Eye') %>% pull(Tissue) %>% unique() %>% length()
num3 <- meta_filter %>% filter(Organ == 'Eye') %>% pull(CellType) %>% unique() %>% length()
scEiaD_data_overview_cap <- fig_cap(name = 'scEiaD_data_overview', caption = glue::glue("Distribution of tissues and cell types in scEiaD. A. tabulation of the number of cells present across {num1} ocular and {num2} non-ocular tissues, B. Number of studies for each ocular tissue. C. Number of cells present across {num3} curated ocular-derived cell types."))

@@

exp_plot_down <- make_exp_plot(input, scEiaD_2020_v01, meta_filter)

input$exp_plot_genes <- up
exp_plot_up <- make_exp_plot(input, scEiaD_2020_v01, meta_filter)
a_legend <- get_legend(exp_plot_down)
plot_grid(plot_grid(exp_plot_down + theme(legend.position="none") + xlab(''),
          exp_plot_up + theme(legend.position="none") + ylab('') + xlab(''), labels = c('a','b')),
          a_legend, ncol = 1, rel_heights = c(1,0.2))
#toc()
```
